---
title: "Kermit Perceptions Rank-Based Test"
author: "Nathaniel Burola"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Nate's first message in the document. 

If you are the collaborator:
- load the tidyverse
- read in the kermit data as 'kermit'
- make some side-by-side histograms of the score.pre for all respondents, separated by the gender column

```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x= Score.pre)) +
  geom_histogram(bins = 4) + 
  facet_wrap(~Gender)

kermit_hist
```

Creator: Perform rank-based comparions using Mann-Whitney U and Wilcoxon-Signed Rank 

Question: Is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents?

```{r}

mwu_kermit <- kermit %>%  
  wilcox.test(Score.pre ~ Gender, data = .)

# Null Hypothesis: There is no significant difference in ranks for male and female respondents 
# HA (Alternative Hypothesis): There IS a significant difference in ranks for male and female respondents 

mwu_kermit
```
There was no significant difference in ranks for male and female respondents (W = 155.5, p = 0.4, alpha = 0.05)

Next question (collaborators):

Is there a significant change in kermit rankings before and after his Bren talk?

```{r}
#HO: There is not a significant difference in ranks for pre- and post talk scores
wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

wsr_kermit

```

There is no significant difference if pre and post talk scores